---
title: "For manuscript"
author: "Anna Moeller"
date: "2023-07-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
library(tidyverse)
```

# Photo summaries

```{r}
df <- readRDS("data/clean/CleanElkandDeer.rds") %>%
  mutate(season = case_when(
    datetime >= as.POSIXct("2017-9-01 00:00:00", tz = "GMT") & 
      datetime <= as.POSIXct("2017-11-30 23:59:59", tz = "GMT") ~ "fall 2017",
    datetime >= as.POSIXct("2018-9-01 00:00:00", tz = "GMT") & 
      datetime <= as.POSIXct("2018-11-30 23:59:59", tz = "GMT") ~ "fall 2018",
    datetime >= as.POSIXct("2019-9-01 00:00:00", tz = "GMT") & 
      datetime <= as.POSIXct("2019-11-30 23:59:59", tz = "GMT") ~ "fall 2019",
    datetime >= as.POSIXct("2017-12-01 00:00:00", tz = "GMT") & 
      datetime <= as.POSIXct("2018-02-28 23:59:59", tz = "GMT") ~ "winter 2017-18",
    datetime >= as.POSIXct("2018-12-01 00:00:00", tz = "GMT") & 
      datetime <= as.POSIXct("2019-02-28 23:59:59", tz = "GMT") ~ "winter 2018-19",
  ))
```
We removed 5 deployments from 2018 that had issues between the photo data and the deploy database. After removing them, we took `r nrow(df)` total motion-sensor photos over the 3 years. 

```{r}
deploy <- readRDS("data/deploy/deploy_fall and winter clean.rds") 
trapdays <- deploy %>% 
  mutate(days = end - start) %>% 
  summarize(trapdays = sum(days))
```
Based on the deploy data, the cameras were functional for `r trapdays` trap days. 

Of our `r nrow(df)` total photos, we took `r length(which(df$ElkCount>0))` photos with elk in them and `r length(which(df$DeerCount>0))` photos of deer. 

### Seasons

We defined fall from September 1 through November 30. We defined winter from December 1 through February 28. Our deer and elk detections were distributed by season as shown in this table: 
```{r}
df %>% 
  group_by(season) %>% 
  summarize(DeerPhotos = sum(DeerCount > 0),
            ElkPhotos = sum(ElkCount > 0)) %>% 
  knitr::kable() # fine but kind of ugly
  # tibble::print.tbl_df() # doesn't work
  # rmarkdown::paged_table() # another option, pretty similar

```

# Proportion of elk points on Peck
```{r, message = F}
onofffiles <- list.files("data/on off peck", full.names = TRUE)
onoff <- map_dfr(onofffiles, read_csv) %>% 
  mutate(date = mdy(GPS_DATE_G),
         year = year(date),
         month = month(date))
# # Monthly 
# onoff %>% 
#   group_by(year, month) %>% 
#   summarize(prop_pts = mean(InorOut)) %>% 
#   knitr::kable()

# Seasonally
onoffseason <- onoff %>%
  mutate(season = case_when(
    month %in% c(9, 10, 11) ~ "Fall",
    month %in% c(12, 1, 2) ~ "Winter"
  )) %>% 
  filter(season %in% c("Fall", "Winter")) %>%
  group_by(year, season) %>%
  summarize(prop_pts_On = mean(InorOut)) 
onoffseason %>%
  knitr::kable()
  
```

# STE
```{r}
# STE deer and elk 
steest <- readRDS("model output/modelrun_dayandnight.rds")  %>% 
  mutate(
    yr = as.numeric(case_when(
      season == "fall17" ~ "2017",
      season == "fall18" ~ "2018",
      season == "fall19" ~ "2019",
      season == "winter1718" ~ "2017",
      season == "winter1819" ~ "2018"
    )),
    seasonyr = case_when(
      season == "fall17" ~ "Fall 2017",
      season == "fall18" ~ "Fall 2018",
      season == "fall19" ~ "Fall 2019",
      season == "winter1718" ~ "Winter 2017-18",
      season == "winter1819" ~ "Winter 2018-19"
    ),
    seasonyr = factor(seasonyr, 
                           levels = c("Fall 2017", 'Winter 2017-18', 'Fall 2018', 'Winter 2018-19', 'Fall 2019')),
    species = if_else(species == "elk", "Elk", "Deer")
  ) %>% 
  select(-season) %>% 
  mutate(season = if_else(grepl("Fall", seasonyr), "Fall", "Winter"))

# Peck abundance estimates
mdcN <- onoffseason %>% 
  ungroup %>%
  mutate(mdcN = rep(c(134, 170, 173), each = 2)) %>% 
  filter(!(year == 2019 & season == "Winter")) %>% 
  mutate(
    seasonyr = factor(c("Fall 2017", "Winter 2017-18", "Fall 2018", 
                        "Winter 2018-19", "Fall 2019"),
                      levels = c("Fall 2017", 'Winter 2017-18', 'Fall 2018', 
                                 'Winter 2018-19', 'Fall 2019')),
    mdc_adjN = mdcN * prop_pts_On,
    species = "Elk"
  ) 
```

### Deer estimates 
```{r}
# Table of estimates 
tmp <- steest %>% 
  arrange(species, seasonyr) %>% 
  select(species, seasonyr, N_PR, Dkm2) 
# deer
tmp %>% 
  filter(species == "Deer") %>% 
  knitr::kable()
```

### Elk estimates 
```{r}
# elk 
tmp %>% 
  filter(species == "Elk") %>% 
  left_join(., mdcN, by = c( "seasonyr", "species")) %>% 
  select(-year, -season) %>% 
  knitr::kable()
```

# Plots of estimates 
```{r}
# Plot deer and elk
p <- ggplot(steest, aes(x = seasonyr, 
                   y = N_PR)) + 
  geom_point(aes(color = season), show.legend = F) + 
  geom_errorbar(aes(x = seasonyr, 
                    ymin = N_PR - 1.96*SE_PR, 
                    ymax = N_PR + 1.96*SE_PR,
                    color = season),
                width = 0,
                show.legend = F) + 
  # Customize the Y axes:
  scale_y_continuous(
    # Features of the first axis
    name = "Abundance on Peck Ranch",
    # Add a second axis and specify its features
    sec.axis = sec_axis( trans=~./96.1614, name=bquote('Density '(km^-2)))
  ) + 
  xlab(element_blank()) + 
  theme_bw() +
  # theme(legend.position = "none") + 
  facet_wrap(~species, scales = "free_y", nrow = 2)

# Add points in Elk
shps <- c("MDC estimate" = 9, "Adjusted MDC estimate"=8)
p + 
  # geom_point(data = mdcN %>% rename(N_PR = mdcN), shape = 9) +
  geom_point(data = mdcN %>% rename(N_PR = mdc_adjN), shape = 8) +
  geom_point(data = mdcN %>% rename(N_PR = mdcN), aes(shape = "MDC estimate")) +
  geom_point(data = mdcN %>% rename(N_PR = mdc_adjN), aes(shape = "Adjusted MDC estimate")) +
  scale_shape_manual(values = shps, 
                     breaks = c("MDC estimate", "Adjusted MDC estimate"),
                     name = element_blank()) +
  theme(legend.position="bottom")



# library(grid)
# library(ggpubr)
# figure <- ggpubr::ggarrange(deerplot + rremove("ylab"), 
#                             elkplot + rremove("ylab"), 
#                             nrow = 2, 
#                             legend = "bottom") 
# ggpubr::annotate_figure(figure, 
#                 left = textGrob("Abundance on Peck Ranch", 
#                                 rot = 90, 
#                                 vjust = 1, 
#                                 gp = gpar(cex = 1.3)),
#                 right = textGrob(bquote('Density '(km^-2)), 
#                                  rot = 270,
#                                   gp = gpar(cex = 1.3)))
  
```

