---
title: "For manuscript"
author: "Anna Moeller"
date: "2023-07-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Photo summaries

```{r, echo = F}
df <- readRDS("data/clean/CleanElkandDeer.rds") %>%
  mutate(season = case_when(
    datetime >= as.POSIXct("2017-9-01 00:00:00", tz = "GMT") & 
      datetime <= as.POSIXct("2017-11-30 23:59:59", tz = "GMT") ~ "fall 2017",
    datetime >= as.POSIXct("2018-9-01 00:00:00", tz = "GMT") & 
      datetime <= as.POSIXct("2018-11-30 23:59:59", tz = "GMT") ~ "fall 2018",
    datetime >= as.POSIXct("2019-9-01 00:00:00", tz = "GMT") & 
      datetime <= as.POSIXct("2019-11-30 23:59:59", tz = "GMT") ~ "fall 2019",
    datetime >= as.POSIXct("2017-12-01 00:00:00", tz = "GMT") & 
      datetime <= as.POSIXct("2018-02-28 23:59:59", tz = "GMT") ~ "winter 2017-18",
    datetime >= as.POSIXct("2018-12-01 00:00:00", tz = "GMT") & 
      datetime <= as.POSIXct("2019-02-28 23:59:59", tz = "GMT") ~ "winter 2018-19",
  ))
```
We removed 5 deployments from 2018 that had issues between the photo data and the deploy database. After removing them, we took `r nrow(df)` total motion-sensor photos over the 3 years. 

```{r, echo = F}
deploy <- readRDS("data/deploy/deploy_fall and winter clean.rds") 
trapdays <- deploy %>% 
  mutate(days = end - start) %>% 
  summarize(trapdays = sum(days))
```
Based on the deploy data, the cameras were functional for `r trapdays` trap days. 

Of our `r nrow(df)` total photos, we took `r length(which(df$ElkCount>0))` photos with elk in them and `r length(which(df$DeerCount>0))` photos of deer. 

### Seasons

We defined fall from September 1 through November 30. We defined winter from December 1 through February 28. Our deer and elk detections were distributed by season as shown in this table: 
```{r, echo = F}
df %>% 
  group_by(season) %>% 
  summarize(DeerPhotos = sum(DeerCount > 0),
            ElkPhotos = sum(ElkCount > 0)) %>% 
  knitr::kable() # fine but kind of ugly
  # tibble::print.tbl_df() # doesn't work
  # rmarkdown::paged_table() # another option, pretty similar

```

# Proportion of points on Peck
```{r, message = F, echo = F}
onofffiles <- list.files("data/on off peck", full.names = TRUE)
onoff <- map_dfr(onofffiles, read_csv) %>% 
  mutate(date = mdy(GPS_DATE_G),
         year = year(date),
         month = month(date))
# # Monthly 
# onoff %>% 
#   group_by(year, month) %>% 
#   summarize(prop_pts = mean(InorOut)) %>% 
#   knitr::kable()

# Seasonally
onoffseason <- onoff %>%
  mutate(season = case_when(
    month %in% c(9, 10, 11) ~ "fall",
    month %in% c(12, 1, 2) ~ "winter"
  )) %>% 
  filter(season %in% c("fall", "winter")) %>%
  group_by(year, season) %>%
  summarize(prop_pts_On = mean(InorOut)) 
onoffseason %>%
  knitr::kable()
  
```

# STE
```{r, echo= F}
# # Peck abundance estimates 
# mdcN <- data.frame(
#   year = c(2017, 2018, 2019),
#   N = c(_, _, _)
# ) <- left_join(onoffseason, .) %>% 
#   mutate(adjN = N * prop_pts_On)

# STE deer and elk 
steest <- readRDS("model output/modelrun_dayandnight.rds")

# Plot
deerD <- ggplot(steest %>% filter(species == "deer")) + 
  geom_point(aes(x = season, 
                 y = Dkm2),
             position = position_dodge(0.2)) + 
  geom_errorbar(aes(x = season, 
                    ymin = Dkm2 - 1.96*SE_km2, 
                    ymax = Dkm2 + 1.96*SE_km2),
                position = position_dodge(0.2),
                width = 0) + 
  theme_classic() + 
  ylab(bquote('Density '(km^-2))) 
elkD <- ggplot(steest %>% filter(species == "elk")) + 
  geom_point(aes(x = season, 
                 y = Dkm2),
             position = position_dodge(0.2)) + 
  geom_errorbar(aes(x = season, 
                    ymin = Dkm2 - 1.96*SE_km2, 
                    ymax = Dkm2 + 1.96*SE_km2),
                position = position_dodge(0.2),
                width = 0) + 
  theme_classic() + 
  ylab(bquote('Density '(km^-2))) 

# Abundance
deerN <- ggplot(steest %>% filter(species =="deer")) + 
  geom_point(aes(x = season, 
                 y = N_PR),
             position = position_dodge(0.2)) + 
  geom_errorbar(aes(x = season, 
                    ymin = N_PR - 1.96*SE_PR, 
                    ymax = N_PR + 1.96*SE_PR),
                position = position_dodge(0.2),
                width = 0) + 
  theme_classic() +  
  ylab('Abundance in Peck Ranch')
elkN <- ggplot(steest %>% filter(species =="elk")) + 
  geom_point(aes(x = season, 
                 y = N_PR),
             position = position_dodge(0.2)) + 
  geom_errorbar(aes(x = season, 
                    ymin = N_PR - 1.96*SE_PR, 
                    ymax = N_PR + 1.96*SE_PR),
                position = position_dodge(0.2),
                width = 0) + 
  theme_classic() +  
  ylab('Abundance in Peck Ranch')

ggpubr::ggarrange(deerD, deerN, elkD, elkN) # species in rows
  
```

